\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-21 WOOT/Files/related_work.tex
defence dcg

\subsection{USB Defence Security}
\label{subsec:usb_defence}
There are already many defenses proposed against BadUSB attacks and a comprehensive investigation of previous work.\cite{sok}.
BadUSB attack requires `D-' and `D+' which have been defined by USB protocol since USB 1.0\cite{usb10},
without these pins, data can't be transferred via USB cable. USB Condom \cite{Condom} proposed a hardware-based solution to prevent data from being transmitted on data channel by adding special hardware between the USB device and host. In this case, `D-' and `D+' are disabled.
However, this method poses a great challenge to easy-to-use property, and once deployed, it will block all USB functions other than charging. Pham et al. \cite{pham2010optimizing} and odix\cite{OLEA} propose scanning function for files on portable USB devices, and can prevent malicious code from attacking host.
There are also some work like TMSUI\cite{yang2015tmsui}, which is based on the unreliable information provided by USB devices during enumeration to defend against BadUSB attack.

Since USB devices may hide their real functionality from the user. GoodUSB\cite{tian2015defending} will report the functionality and identity of the device to the user and the user needs to explicitly authorize. On this basis, GoodUSB loads the corresponding driver for the device, and device can not request other drivers during enumeration or usage. This restricts the device to load only the drivers allowed by the user, but does not prevent the device from using available drivers to attack. For example, a malicious keyboard can type commands without the user's knowledge after enumeration. Because from the user's perspective, he must permit a USB-based keyboard the corresponding drivers to allow himself to authorize, but once the drivers are loaded, the malicious USB-based keyboard can also automatically type in commands. What's more, in GoodUSB, VM is deployed in host to interact with the USB device to detect malicious behavior like automatic execution of code.

Windows Defender ATP\cite{windenfenderwhite} maintains a whitelist of USB devices, only if one USB device is in the white list can it interact with host. This prevents all interactions between untrusted devices and the host. But this reduces the easy-to-use property and requires users to have a certain safety awareness. For example, a naive user may add the USB device he/she found outdoors to his/her whitelist without precautions. Mohammadmoradi et al\cite{mohammadmoradi2018making} propose generating unique fingerprint based on the features and functions of the USB device to build such a whitelist.

Neuner et al.\cite{neuner2018usblock} prevent USB key injection attacks from malicious flash drive by analyzing temporal characteristics of BadUSB-like attacks. This defense mechanism is successful as the attacker cannot obtain the screen of the host using BadUSB, so that the malicious device can only inject instructions in a very short time to prevent the user from discovering. This causes the typing characteristics of BadUSB devices to be abnormal and detectable.

Some composite anti-virus systems, like Windows Defender ATP\cite{windenfender} and Metascan\cite{OPSWAT} can sanitize the malicious files in the device to stop malware. However, Metascan warned users to be wary of the device plugged into the computer, since there is currently no way to ensure absolutely security.

For those attacks that use the USB cable to peek at the device screen while the user is charging the mobile device, Meng et al\cite{meng2018252} detect potential attacks by analyzing changes in the usage of CPU and GPU.

We summarize the former effort in USB attack and defense in Table~\ref{table:attack_vs_defense}, which illustrated the effectiveness of each defense against various attacks including our \tool.
\begin{table*}
	\centering
	\begin{tabular}{|c|c|c|c|c|c|c|}

>>>>

\subsection{USB Defence Security}
\label{subsec:usb_defence}
There are already many defenses proposed against BadUSB attacks and a comprehensive investigation of previous work.\cite{sok}.
BadUSB attack requires `D-' and `D+' which have been defined by USB protocol since USB 1.0\cite{usb10}.
Without these pins, data can't be transferred via USB cable. USB Condom \cite{Condom} proposed a hardware-based solution to prevent data from being transmitted on data channel by adding special hardware between the USB device and host. This hardware can cut off the `D-' and `D+' and allow only power pins.
However, this method poses a great challenge to easy-to-use property, and once deployed, it will block all USB functions other than charging.

Under the premise of ensuring the normal operation of all USB pins, some work improve the security of connection establishment.
Windows Defender ATP\cite{windenfenderwhite} maintains a whitelist of USB devices, only if one USB device is in the whitelist can it interact with host through data channel. This prevents all interactions between untrusted devices and the host. But this requires users to have a certain safety awareness. For example, a naive user may add the USB device from unknown sources to his/her whitelist without precaution. Mohammadmoradi et al\cite{mohammadmoradi2018making} propose a strategy to generate a whitelist automatically. Based on the features and functions of the USB devices, Mohammadmoradi et al generate unique fingerprint to each device and classify them. There are also some work like TMSUI\cite{yang2015tmsui}, which is based on the unreliable information provided by USB devices during enumeration to defend against BadUSB attack. 
However, this work relies on the information provided by the device during enumeration. Some USB devices may hide their real functionality from the user.
GoodUSB\cite{tian2015defending} will report the functionality and identity of the device to user and user needs to explicitly authorize. On this basis, GoodUSB loads the corresponding driver for the device, and device can not request other drivers during enumeration or usage. This restricts the device to load only the drivers allowed by the user, but does not prevent the device from using available drivers to attack. For example, a malicious keyboard can type commands without the user's knowledge after enumeration. Because from the user's perspective, he/she must permit a USB-based keyboard the corresponding drivers by authorizing them him/herself. But once the drivers are loaded, the malicious USB-based keyboard can also automatically type in commands.

When the USB device is normally enumerated and can interact with the host, there are also some defenses. 
Neuner et al.\cite{neuner2018usblock} prevent USB key injection attacks from malicious flash drive by analyzing temporal characteristics of BadUSB-like attacks. This defense mechanism is effective as the attacker cannot obtain the screen of the host using BadUSB. In this case, the malicious device can only inject instructions in a very short time to reduce the risk of being discovered. It leads to the typing characteristics of BadUSB devices to be abnormal and detectable. Apart from key injection attacks, malicious file injection can also be detected. Pham et al. \cite{pham2010optimizing} and odix\cite{OLEA} propose scanning function for files on portable USB devices, and can prevent malicious code from attacking host. What's more, in GoodUSB, VM is deployed in host to interact with the USB device to detect malicious behavior like automatic execution of code. In addition to injection attacks, data theft attack is also one of the focuses of the academic community. When the screen data of the mobile device is stolen while charging, the power consumption of the mobile device will change. So Meng et al\cite{meng2018252} detect potential attacks by monitoring and analyzing changes in the usage of CPU and GPU.

Some composite anti-virus systems, like Metascan\cite{OPSWAT}, incorporates some defenses. Metascan can verify digital signature of USB device, sanitize the malicious files in the device to stop malware, and deploy kiosks to protect security-sensitive organizations. However, Metascan also warned users to be cautious of the device plugged into the host, since there is no way to ensure absolute security.

\linyou{logic connection and pros/cons}

We summarize the former effort in USB attack and defense in Table~\ref{table:attack_vs_defense}, which illustrates the effectiveness of each defense against various attacks including our \tool.
\begin{table*}
	\centering
	\begin{tabular}{|c|c|c|c|c|c|c|}
